Speeding up prediction performance of the BDT-based models

### 2017-11-09 acat_paper/paper.tex
Added graphics

We have used the dataset and the model from [@ likhomanenko2015lhcb]. Number of features in the dataset is 10, the model was trained on 5000 trees with a number of the buckets 64. We compared our algorithm for constructing Decision Tensors Ensemble with trivial approach: training a small number of trees but with high value of the training speed.
For this we divided the data set into three parts: training (50\%), test (25\%) and validation (25\%). We trained the models on the training sample, then used the test for the selection of the best models under given constraints.

@@

The figure of merit we've taken also from [@_likhomanenko2015lhcb], which is the area under the ROC curve where False Positive Rate less than 0.05. For the convenience, we have normalized this metric so that its maximum value (with an ideal model) is equal to 1.

@@

Figure 1 shows the dependence of the quality on the number of lookups. Chart 2 shows the dependence of the quality vs the total inference time at the full validation dataset. Table 3 shows properties of the models trained in the process.

TODO: добавить графики из презентации

>>>>

We have used the dataset and the model from [2]. Number of features in the dataset is 10, the model was trained on 5000 trees with a number of the buckets 64. We compared our algorithm for constructing Decision Tensors Ensemble with trivial approach: training a small number of trees but with high value of the training speed.
For this we divided the data set into three parts: training (50\%), test (25\%) and validation (25\%). We trained the models on the training sample, then used the test for the selection of the best models under given constraints.

@@

The figure of merit we've taken also from [2], which is the area under the ROC curve where False Positive Rate less than 0.05. For the convenience, we have normalized this metric so that its maximum value (with an ideal model) is equal to 1.

@@

Figure 1 shows the dependence of the quality on the number of lookups. Figure 2 shows the dependence of the quality vs the total inference time at the full validation dataset. Table 1 shows properties of the models trained in the process.

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{"lookups.png"}
\caption{Lookups count versus FOM for different models sizes}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{"times.png"}
\caption{Application time versus FOM for different models sizes}
\end{center}
\end{figure}

\begin{table}[h]
\caption{\label{tabone}Properties of the some models trained in the process}

\begin{center}
\lineup
\begin{tabular}{*{4}{l}}
\br
Model & Roc & Time, ms & Size, Mb \cr
\mr
catboost-5000 & $0.6004$ & $10000$ & $<5$ \cr
catboost-100 & $0.589$ & $160$ & $<5$ \cr
catboost-75 & $0.5808$ & $125$ & $<5$ \cr
catboost-10 & $0.5336$ & $30$ & $<5$ \cr
big dte-6 & $0.5952$ & $180$ & $1000$ \cr
big dte-3 & $0.5938$ & $145$ & $1000$ \cr
big dte-2 & $0.5844$ & $70$ & $1000$ \cr
small dte-2 & $0.5794$ & $55$ & $150$ \cr
dte-1 & $0.5618$ & $30$ & $150$ \cr
\br
\end{tabular}
\end{center}
\end{table}
